Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-21 manuscript/manuscript.Rmd
added discussion on drl policy and time-series

Moreover, in an attempt to further understand the relationship between the different management strategies considered, Fig. **TBD** presents the time-series of a representative episode for each strategy.
Here we see a pattern that arises throughout the entire dataset---early episode ends are largely due to near-extinctions of $Z$.

>>>>

We notice that the DRL-derived policy has similarities to a constant escapement policy.
Here, the key difference is that the escapement value for each of the fished species is sensitive to variations in the other populations. 
This can be seen as a color gradients in the plots of $(X, M_X)$ and $(Y, M_Y)$, where the gradient corresponds to differing values of $Z$.
Moreover, this can be seen as an anti-correlation in the plot of $(X, M_Y)$---for optimal constant escapement, $M_Y$ is uncorrelated to $X$.

The sensitivity of the policy to, e.g., the values of $Z$ can be seen in the sample time series displayed in Fig. **TBD**.
Here, we can see that species $Z$ becomes endangered due to harvesting for all management strategies.
The DRL-based strategy, however, is sensitive to the values of $Z$ and can respond accordingly by scaling the fishing effort with the value of $Z$.
In particular, the policy responds to periods of low values of $Z$ by restricting fishing on $X$ and $Y$, thus promoting $Z$'s growth.
This pattern is rather common among the whole dataset---early episode ends are largely due to near-extinctions of $Z$ for all management strategies.
